Displacement of fishing effort by Large Scale Marine Protected Areas[^*]

### 2018-10-21 rmd/Manuscript.Rmd
Updated manuscritp, sent to John

We use daily fishing hours, daily proportion of fishing vs. non-fishing hours, and daily distance traveled (km). We compare our variable of interest before and after the implementation of PIPA using a Difference-in-Differences approach, where we track the variable of interest for vessels described in the previous section. Our specification is the following:

@@

- Distance traveled
- Non-fishing hours at sea
- Monthly crowdnes??
- Repeat raster exercise for Revillagigedo and other recently implemented LSMPAs. It would be great to have a pannel figure of 3 or 4 other LSMPAs that show wher effort was and where it went to generalize our results.
- John talked about this being relevant to Palau (their upcoming LSMPA). We might want to talk about where the vessels that are there would go.

@@

## Other model specifications for purse seiners

We include a second degree polynomial for years as:

$$
y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \omega Y_t + \Omega Y_t^2 + \epsilon_{i,t}
$$

```{r}
model_data <- readRDS(file = here::here("data", "effort_by_vessel.rds")) %>%
  filter(year < 2018,
         baci_strict,
         gear == "purse_seines") %>% 
  mutate(post = post * 1,
         treated = treated * 1,
         mmsi_c = as.factor(mmsi))

m1 <- lm(hours ~ post*treated, data = model_data)
m2 <- lm(hours ~ post*treated + month_c, data = model_data)
m3 <- lm(hours ~ post*treated + month_c + year_c, data = model_data)
m4 <- lm(hours ~ post*treated + month_c + year_c + flag, data = model_data)
```

```{r, results = "asis"}
models <- list(m1, m2, m3, m4)

stargazer::stargazer(models,
                     se = commarobust::makerobustseslist(models),
                     t.auto = T,
                     p.auto = T,
                     type = "latex",
                     omit = c("flag", "year", "month"),
                     add.lines = list(c("Month FE", "No", "Yes", "Yes", "Yes"),
                                      c("Year FE", "No", "No", "Yes", "Yes"),
                                      c("Flag FE", "No", "No", "No", "Yes")),
                     omit.stat = c("adj.rsq", "f", "ser"),
                     header = F,
                     title = "\\label{tab:purse}Fishing hours from GFW for purse_seiners. Asterisks indicate significance levels. Numbers in parentheses represent heteroskedastic-robust standard errors.")
```

@@

@@

## Rasterized regions

>>>>

We use daily fishing hours, daily proportion of fishing vs. non-fishing hours, daily distance traveled (km), distance from shore (km) and distance from port(km)\footnote{Results are presented for fishing hours, bur preliminary results for distance form shore and distance from port are shown in Tables \ref{tab:dist_shore} and \ref{tab:dist_port}}. We compare our variable of interest before and after the implementation of PIPA using a Difference-in-Differences approach, where we track the variable of interest for vessels described in the previous section. Our specification is the following:

@@

- Distance traveled
- Non-fishing hours at sea
- Monthly crowdnes (same approach as now, but monthly instead of yearly)
- Number of vessels per cell as another measure of crowdness (this is a more real one)
- Repeat raster exercise for Revillagigedo and other recently implemented LSMPAs. It would be great to have a pannel figure of 3 or 4 other LSMPAs that show wher effort was and where it went to generalize our results.
- John talked about this being relevant to Palau (their upcoming LSMPA). We might want to talk about where the vessels that are there would go.

@@

@@

## Other measures of change in behavior

Global Fishing Watch data includes two variables of interest that are readily available: distance from shore and distance from port. We use these as variables of interest and perform the following regression:

$$
y = \beta_1Year + \beta_2Treated + \beta_3Year \ Treated + \epsilon
$$

Where $y$ is our variable of interest, $Year$ represent year dummies, with 2012 as the reference level, and $Treated$ indicates wether a vessel belongs to the treated or control group.

### Distance from shore

```{r}
vessel_tracks <- readRDS(file = here::here("raw_data", "vessel_tracks.rds")) %>% 
  filter(year < 2018,
         fishing,
         gear == "purse_seines") %>% 
  mutate(year_c = as.factor(year))

```

```{r, results = "asis"}
lm(distance_from_shore ~ year_c * treated, data = vessel_tracks) %>% 
  stargazer::stargazer(se = commarobust::makerobustseslist(.),
                       pauto = T,
                       tauto = T, title = "\\label{tab:dist_shore}Regression results for distance from shore. Numbers in parentheses are heteroskedastic-robust standard errors.",
                       intercept.bottom = F,
                       type = "latex",
                       header = F)
```

### Distance from ports

```{r, results = "asis"}
lm(distance_from_port ~ year_c * treated, data = vessel_tracks) %>% 
  stargazer::stargazer(se = commarobust::makerobustseslist(.),
                       pauto = T,
                       tauto = T, title = "\\label{tab:dist_port}Regression results for distance from shore",
                       intercept.bottom = F,
                       type = "latex",
                       header = F)
```

@@

### Rasterized regions
